---
title: "Leaflet"
date: "March 29, 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
```

## Overview

This is the week 2 assignment for the Developing Data Products course.   Our task is to create a web page using R Markdown that features a map created with Leaflet. As per the assignment, the webpage contains the date that the document was created and it contains a map created with Leaflet.    


## Plot US Landmarks

I made a csv with landmarks and their coordinates.   <b> Step 1 </b> is to read in the CSV.

```{r readcsv}
# Original list from  https://www.latlong.net/category/monuments-236-46.html
df <- read.csv("USLandmarks.csv", stringsAsFactors = F)
str(df)
```

Next, in <b> Step 2 </b> we'll plot these landmarks with leaflet.

```{r leaflet}
library(leaflet)
m <- leaflet() %>% addTiles() 
for (i in 1:nrow(df)) {
        m <- m %>% addMarkers(lng=df$Longitude[i], lat=df$Latitude[i], popup=df$Place[i])
}
m
```

The data and code for this are stored at https://github.com/anon-813/data_products_wk2.
